Effects of CHILDREN's programs

### 2020-02-27 paper.tex
commit compile

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 22:26:53 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccccc}
  \hline
 & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
1 & 2011 & 3748.0 &  & 52 &  \\ 
  2 & 2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  3 & 2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  4 & 2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  5 & 2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  6 & 2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  7 & 2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  8 & 2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{fundamentalDynamics}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 10:27:21 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
  \label{lessIllOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 10:27:22 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
  \label{dietaryOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 10:27:22 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
  \label{appreciateOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 10:27:23 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth} 
  \label{selfworthOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 10:27:23 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise} 
  \label{dayToDayOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -3.543 & 0.343 & -10.330 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -0.736 & 0.132 & -5.563 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.764 & 0.157 & 11.249 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00003 & 0.00001 & -4.070 & 0.00005 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

In addition to the factor analysis which is described in section 6, we would like to introduce to a another dimensionality reduction method called partition. This method was developped by Millstein et. al in the context of genome analysis.

The partition approach partitions data into subsets of related features. It then  summarizes each subset into one new feature. By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}. A function g is implemented using the arithmetic mean. In contrast to methods like the factor analysis, if a feature is identified as related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity. What is as well different is the information loss constraint. It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \parencite[p.677]{Millstein.2020}.

In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent. It might be meaningful to decide to use only one of the featured variables in a reduced variable (or a summarizing one) for future surveys to avoid redundancy.

Table \ref{partitionmeals} shows the obtained results of the dimensionality reduction for the variables of the Lunch program. It displays 10 variables which haven't been reduced, and 5 reduced variables with a number of featured variables.

Table \ref{partitiontrips} shows the partitioned results for the variables of the Trips program. Here, 12 variables haven't been reduced, and a number of featured variables are summarized to 3 reduced variables.

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 22:27:24 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccc}
  \hline
 & Variable, Meals & Mapping, Meals & Information, Meals \\ 
  \hline
1 & participateMore & participateMore & 1.00 \\ 
  2 & tasksLunch & tasksLunch & 1.00 \\ 
  3 & ownIdeas & ownIdeas & 1.00 \\ 
  4 & stayLonger & stayLonger & 1.00 \\ 
  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
  7 & foodCulture & foodCulture & 1.00 \\ 
  8 & lessIll & lessIll & 1.00 \\ 
  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
  11 & addressProblems & addressProblems & 1.00 \\ 
  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
  23 & reduced\_var\_3 & proud & 0.43 \\ 
  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Meals} 
\label{partitionmeals}
\end{table}
% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 22:27:24 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccc}
  \hline
 & Variable, Trips & Mapping, Trips & Information, Trips \\ 
  \hline
1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
  5 & tripsBudget & tripsBudget & 1.00 \\ 
  6 & tripsMoney & tripsMoney & 1.00 \\ 
  7 & tripsReview & tripsReview & 1.00 \\ 
  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
  9 & tripsMobility & tripsMobility & 1.00 \\ 
  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Trips} 
\label{partitiontrips}
\end{table}

\subsection{A4: OLS Regressions}

% # <<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
% # 
% # lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
% # lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
% # ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
% # td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
% # sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
% # dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
% # tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
% # tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
% # @

% <<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
% #expanded model less ill 
% 
% lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
% lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
% elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.Rds")
% @

\subsection{A5: DID Regression Results}

@@

>>>>

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 23:03:35 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccccc}
  \hline
 & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
1 & 2011 & 3748.0 &  & 52 &  \\ 
  2 & 2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  3 & 2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  4 & 2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  5 & 2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  6 & 2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  7 & 2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  8 & 2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{fundamentalDynamics}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:04:02 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
  \label{lessIllOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:04:02 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
  \label{dietaryOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:04:03 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
  \label{appreciateOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:04:04 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth} 
  \label{selfworthOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 11:04:04 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise} 
  \label{dayToDayOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -3.543 & 0.343 & -10.330 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -0.736 & 0.132 & -5.563 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.764 & 0.157 & 11.249 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00003 & 0.00001 & -4.070 & 0.00005 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

In addition to factor analysis, we have conducted another dimensionality reduction exercise called partition. This method is due to \textcite{Millstein.2020}. The authors propose it in the context of genome analysis, where high dimensionality is a perennnial statistical problem.

Unlike exploratory factor analysis, the partition approach is deliberately designed to establish a one-to-one correspondence between the measured variables and presumed underlying variables. This means that the set of all variables is partitioned into subsets. A subset may contain only one variable. The deterministic partition algorithm is constructed in such a way as to ensure that there is a high correlation within subsets and a small correlation between. One can influence the number of subsets by manipulating a threshold limiting information loss.

We use a threshold of 0.4, which means that the variables in each subset explain each other to at least 40 percent. It might be meaningful to decide to use only one of the featured variables in a reduced variable (or a summarizing one) for future surveys to avoid redundancy.

Table \ref{partitionmeals} shows the obtained results of the partition method for the variables of the Lunch program. It displays 10 variables which have not been reduced, and 5 reduced variables with a number of featured variables.

Table \ref{partitiontrips} does the same for the variables of the Trips program. Here, 12 variables have not been reduced, and a number of featured variables are summarized to 3 reduced variables.

It is our impression that the partition technique results in a highly intuitive dimensionality reduction.

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 23:04:04 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccc}
  \hline
 & Variable, Meals & Mapping, Meals & Information, Meals \\ 
  \hline
1 & participateMore & participateMore & 1.00 \\ 
  2 & tasksLunch & tasksLunch & 1.00 \\ 
  3 & ownIdeas & ownIdeas & 1.00 \\ 
  4 & stayLonger & stayLonger & 1.00 \\ 
  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
  7 & foodCulture & foodCulture & 1.00 \\ 
  8 & lessIll & lessIll & 1.00 \\ 
  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
  11 & addressProblems & addressProblems & 1.00 \\ 
  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
  23 & reduced\_var\_3 & proud & 0.43 \\ 
  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Meals} 
\label{partitionmeals}
\end{table}
% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 23:04:04 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccc}
  \hline
 & Variable, Trips & Mapping, Trips & Information, Trips \\ 
  \hline
1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
  5 & tripsBudget & tripsBudget & 1.00 \\ 
  6 & tripsMoney & tripsMoney & 1.00 \\ 
  7 & tripsReview & tripsReview & 1.00 \\ 
  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
  9 & tripsMobility & tripsMobility & 1.00 \\ 
  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Trips} 
\label{partitiontrips}
\end{table}

\subsection{A4: DID Regression Results}

@@

\begin{figure}
  \caption{The trend of weekly cooks over time}
  \label{weeklyCooks_Trend}

{\centering \includegraphics[width=0.8\textwidth]{figure/WeeklyCooks-1}

\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012. The y-axis represents the average answers from the organizations regarding to the weekly cooks they made. The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line. Additionally, the linear trends of both groups are included as the straight lines.}
\end{figure}

\begin{figure}
  \caption{The Trend of monthly cooks over time}
  \label{monthlyCooks_Trend}

{\centering \includegraphics[width=0.8\textwidth]{figure/MonthlyCooks-1}

\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012. The y-axis represents the average answers from the organizations regarding to the monthly cooks they made. The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line. Additionally, the linear trends of both groups are included as the straight lines.}
\end{figure}
